Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-16 write-ups/PLDI/paper.tex
Space.

We discuss our experience porting irregular algorithms to cooperative kernels (\mysec\ref{sec:portingalgorithms}) and discuss the GPUs on which we evaluate these applications (\mysec\ref{sec:gpus}).  For these GPUs, we report on experiments to determine non-cooperative workloads that model the requirements of various graphics rendering tasks (\mysec\ref{sec:sizingnoncoop}).  We then examine the overhead associated with moving to cooperative kernels when multitasking is \emph{not} required (\mysec\ref{sec:overhead}), as well as the responsiveness and throughput observed when a cooperative kernel is multi-tasked with non-cooperative workloads (\mysec\ref{sec:responsiveness}).

\subsection{Porting Irregular GPU Algorithms}\label{sec:portingalgorithms}

@@

From the Lonestar suite we omit two applications that use global barriers:
dmr has been shown to be unstable across GPU vendors~\cite{DBLP:conf/iwocl/SorensenD16}, and mst is trivially short-running so that it is not
interesting for our multitasking approach.
%
These exceptions aside, we have handled all the available OpenCL
implemenatinos of irregular algorithms that we are aware of, plus two
easy-to-adapt CUDA algorithms (the workstealing examples).

\subsection{The GPUs we Tested}\label{sec:gpus}

@@

\section{Graphs for Multitasking Experiments}\label{appendix:extragraphhs}

>>>>

We discuss our experience porting irregular algorithms to cooperative kernels and describe the GPUs on which we evaluate these applications (\mysec\ref{sec:portingalgorithms}).  For these GPUs, we report on experiments to determine non-cooperative workloads that model the requirements of various graphics rendering tasks (\mysec\ref{sec:sizingnoncoop}).  We then examine the overhead associated with moving to cooperative kernels when multitasking is \emph{not} required (\mysec\ref{sec:overhead}), as well as the responsiveness and throughput observed when a cooperative kernel is multi-tasked with non-cooperative workloads (\mysec\ref{sec:responsiveness}).

\subsection{Applications and GPUs}\label{sec:portingalgorithms}

@@

From the Lonestar suite we omit two applications that use global barriers:
dmr has been shown to be unstable across GPU vendors~\cite{DBLP:conf/iwocl/SorensenD16}, and mst is trivially short-running so that it is not
interesting for our multitasking approach.

@@

\section{Graphs for Multitasking Experiments}\label{appendix:extragraphs}
